Interval Probability for Fuzzy Quantum Theories

### 2016-06-09 prob.tex
prob.tex \subsection{Quantum Interval-valued Probabilities Measures} keep typing...

Vourdas observed that equation (\ref{eq:Kolmogorov}) is similar to
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear subspaces, and $\Pi$
maps a linear subspace to its projection operator. After apply the
Born rule on both sides, we get an equation about the probabilities
\begin{equation}
\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\Tr\left(\rho\Pi\left(S_{1}\vee S_{2}\right)\right)-\Tr\left(\rho\Pi\left(S_{1}\right)\right)-\Tr\left(\rho\Pi\left(S_{2}\right)\right)+\Tr\left(\rho\Pi\left(S_{1}\wedge S_{2}\right)\right)\textrm{ .}\label{eq:quantum-additivity}
\end{equation}
Given the density matrix~$\rho$, the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
is then analog to the sign of $\delta\left(E_{1},E_{2}\right)$ since
the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
is non-zero when $S_{1}$ and $S_{2}$ does not commute so that $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
is not always zero. Vourdas then considered the pair $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
and $\Tr\left(\rho\Pi\left(S_{2}\right)\right)$ are lower or upper
probabilities depending on the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$.
Although Vourdas' idea is clear, the approach does not exactly fit
the idea. First, when we measure a physical quantity, we consider
the eigenspaces of an observable which always commute. According to
Vourdas' definition, $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
is then always an Kolmogorov probability within one measurement process.
Second, if we adopt the frequency interpretation as in section \ref{subsec:Measuring-Probabilities:-Buffon},
consider the following two-qubit example.

>>>>

Vourdas observed that equation (\ref{eq:Kolmogorov}) is similar to
\[
\mathfrak{D}\left(S_{1},S_{2}\right)=\Pi\left(S_{1}\vee S_{2}\right)-\Pi\left(S_{1}\right)-\Pi\left(S_{2}\right)+\Pi\left(S_{1}\wedge S_{2}\right)\textrm{ ,}
\]
where $S_{1}$ and $S_{2}$ are arbitrary linear subspaces, and $\Pi$
maps a linear subspace to its projection operator. After apply the
Born rule on both sides, we get an equation about the probabilities
\begin{equation}
\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)=\Tr\left(\rho\Pi\left(S_{1}\vee S_{2}\right)\right)-\Tr\left(\rho\Pi\left(S_{1}\right)\right)-\Tr\left(\rho\Pi\left(S_{2}\right)\right)+\Tr\left(\rho\Pi\left(S_{1}\wedge S_{2}\right)\right)\textrm{ .}\label{eq:quantum-additivity}
\end{equation}
Given the density matrix~$\rho$, the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
is then analog to the sign of $\delta\left(E_{1},E_{2}\right)$ since
the non-additivity operator~$\mathfrak{D}\left(S_{1},S_{2}\right)$
is non-zero when $S_{1}$ and $S_{2}$ does not commute so that $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$
is not always zero. Vourdas then considered the pair $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
and $\Tr\left(\rho\Pi\left(S_{2}\right)\right)$ are lower or upper
probabilities depending on the sign of $\Tr\left(\rho\mathfrak{D}\left(S_{1},S_{2}\right)\right)$.
Although Vourdas' idea is clear, the approach does not exactly fit
the idea. First, when we measure a physical quantity, we consider
the eigenspaces of an observable which always commute. According to
Vourdas' definition, $\Tr\left(\rho\Pi\left(S_{1}\right)\right)$
is then always an Kolmogorov probability within one measurement process.
Second, if we adopt the frequency interpretation as in section \ref{subsec:Measuring-Probabilities:-Buffon},
and implement our one-qubit example in the Stern-Gerlach experiment.
Let $S_{1}=\left\{ \lambda\ket{0}\middle|\lambda\in\C\right\} $ and
$S_{2}=\left\{ \lambda\ket{\ps}\middle|\lambda\in\C\right\} $.
